# Analysis for publication "Zooming into STEM: Designing Curriculum Around Guest Presentations in an Online After-School STEM Program for Title I Elementary Students"

## Set-up

```{r}

# Clear environment

rm(list = ls())

```

```{r}

# Load necessary libraries

library(readr)
library(tidyr)
library(tm)
library(wordcloud)
library(ggwordcloud)
library(wesanderson)
library(stringr)
library(readr)
library(gt)
library(conflicted)

library(dplyr)
library(ggplot2)

```

## Speaker survey analyses

```{r}

# Load data

speaker_survey_2023_2025_raw <- read_csv(file = "../data/Speaker_Surveys_2021-2024.csv")

head(speaker_survey_2023_2025_raw)


```

### Data cleaning

```{r}

speaker_survey_2023f_raw <- speaker_survey_2023_2025_raw %>%
  mutate(Timestamp = mdy_hms(Timestamp)) %>%
  dplyr::filter(Semester == "Fall_2023")


# Create a lookup table to convert original column names (survey questions) to their shortened names
question_lookup <- data.frame(
  Original_Column = colnames(speaker_survey_2023f_raw),
  Shortened_Column = c(
    "Semester",
    "Timestamp",                
    "End_Timestamp",            
    "Response_ID",              
    "Name",                     
    "Subject",                  
    "Speaker_Before",           
    "Overall_Rating",           
    "Inspire_Info",             
    "Hands_On_Activities",      
    "Background_Knowledge",     
    "Engagement_Enjoyment",     
    "Staff_Helpfulness",        
    "Went_Well",                
    "Went_Not_Well",            
    "Speaker_Quote",            
    "Future_Suggestions",
    "Anything_Else"                     
  )
)

speaker_survey_2023_2025_raw <- speaker_survey_2023_2025_raw %>%
  rename_with(~ question_lookup$Shortened_Column[match(., question_lookup$Original_Column)])


speaker_survey_2023f_clean <- speaker_survey_2023f_raw %>%
  rename_with(~ question_lookup$Shortened_Column[match(., question_lookup$Original_Column)])

head(speaker_survey_2023f_clean)


```

```{r}

# Summary table of speaker survey results

scale_cols <- c("Background_Knowledge", "Engagement_Enjoyment", "Staff_Helpfulness")

speaker_survey_2023f_clean %>%
  mutate(across(all_of(c("Overall_Rating", scale_cols)), as.numeric)) %>%
  mutate(across(all_of(scale_cols), ~ . * 2)) %>%
  select(Overall_Rating, all_of(scale_cols)) %>%
  pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
  group_by(Question) %>%
  summarize(Mean = mean(Response, na.rm = TRUE),
            SD   = sd(Response, na.rm = TRUE),
            n    = n(), .groups = "drop") %>%
  gt() %>%
  tab_header(title = "Lesson Ratings by Question",
             subtitle = "Fall 2023 Speaker Feedback") %>%
  cols_label(Question = "Survey Question",
             Mean = "Mean", SD = "Std Dev", n = "n") %>%
  fmt_number(columns = c(Mean, SD), decimals = 2) %>%
  tab_footnote("Scaled to max 10.",
               locations = cells_column_labels(c(Mean, SD)))



```

### Comparing speaker surveys across semesters

#### Box-and-whisker plots

```{r}

# Clean data
speaker_ratings_long <- speaker_survey_2023_2025_raw %>%
  dplyr::filter(Semester %in% c("Spring_2021", "Spring_2022", "Fall_2023")) %>%
  mutate(across(all_of(scale_cols), as.numeric),
         across(all_of(scale_cols), ~ . * 2),
         Semester = factor(Semester, levels = c("Spring_2021", "Spring_2022", "Fall_2023", "Spring_2024"))) %>%
  select(Semester, all_of(scale_cols)) %>%
  pivot_longer(cols = all_of(scale_cols), names_to = "Metric", values_to = "Rating") %>%
  drop_na()


n_labels_ratings <- speaker_ratings_long %>%
  group_by(Semester, Metric) %>%
  summarize(label = paste0("n = ", n()), .groups = "drop")

# Set colors
okabe_ito <- palette.colors(palette = "Okabe-Ito")
semester_colors <- c(
  "Spring_2021" = okabe_ito[2],
  "Spring_2022" = okabe_ito[3],
  "Fall_2023"   = okabe_ito[4],
  "Spring_2024" = okabe_ito[5]
)


# Plot
ggplot(speaker_ratings_long, aes(x = Semester, y = Rating, fill = Semester)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(alpha = 0.3, width = 0.2) +
  geom_text(data = n_labels_ratings, aes(x = Semester, y = -Inf, label = label),
            vjust = -0.5, size = 3, inherit.aes = FALSE) +
  facet_wrap(~ Metric, labeller = as_labeller(c(
    Background_Knowledge = "Background Knowledge",
    Engagement_Enjoyment = "Engagement & Enjoyment",
    Staff_Helpfulness    = "Staff Helpfulness"
  ))) +
  scale_fill_manual(values = semester_colors) +
  scale_x_discrete(labels = c("Spring_2021" = "Spring 2021",
                               "Spring_2022" = "Spring 2022",
                               "Fall_2023"   = "Fall 2023",
                               "Spring_2024" = "Spring 2024")) +
  ylim(5, 10) +
  labs(title = "Speaker Ratings by Semester",
       x = "", y = "Rating (out of 10)") +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1))

ggsave("../outputs/speaker_ratings_by_semester.png", width = 10, height = 5, dpi = 300)

```

### T-test speaker surveys across semesters

```{r}

# Create era grouping: 2021/2022 vs 2023
speaker_ratings_wide <- speaker_survey_2023_2025_raw %>%
  dplyr::filter(Semester %in% c("Spring_2021", "Spring_2022", "Fall_2023")) %>%
  mutate(across(all_of(scale_cols), as.numeric),
         across(all_of(scale_cols), ~ . * 2),
         time_period = if_else(Semester %in% c("Spring_2021", "Spring_2022"), "2021-2022", "2023"))

# Background Knowledge
before_bg <- speaker_ratings_wide %>% 
  dplyr::filter(time_period == "2021-2022") %>% 
  pull(Background_Knowledge)

after_bg  <- speaker_ratings_wide %>% 
  dplyr::filter(time_period == "2023") %>% 
  pull(Background_Knowledge)

t.test(before_bg, after_bg, paired = FALSE)


# Engagement & Enjoyment
before_ee <- speaker_ratings_wide %>% 
  dplyr::filter(time_period == "2021-2022") %>% 
  pull(Engagement_Enjoyment)

after_ee  <- speaker_ratings_wide %>% 
  dplyr::filter(time_period == "2023") %>% 
  pull(Engagement_Enjoyment)

t.test(before_ee, after_ee, paired = FALSE)


# Staff Helpfulness
before_sh <- speaker_ratings_wide %>% 
  dplyr::filter(time_period == "2021-2022") %>% 
  pull(Staff_Helpfulness)

after_sh  <- speaker_ratings_wide %>% 
  dplyr::filter(time_period == "2023") %>% 
  pull(Staff_Helpfulness)

t.test(before_sh, after_sh, paired = FALSE)



sum(!is.na(before_bg))
sum(!is.na(after_bg))

```

### Speaker comments word cloud

```{r}

# Speaker Survey open-ended questions word cloud

relevant_columns <- speaker_survey_2023f_clean %>%
  select(Inspire_Info, Hands_On_Activities, Went_Well, Went_Not_Well, Speaker_Quote, Future_Suggestions)

# Combine text data from the relevant columns
text_data <- apply(relevant_columns, 1, paste, collapse = " ")

# Create a text corpus
corpus <- Corpus(VectorSource(text_data))

# Define additional stopwords to remove
custom_stopwords <- c("andrea", "charles")

# Combine with default English stopwords
all_stopwords <- c(stopwords("english"), custom_stopwords)

# Preprocess the text data
corpus <- tm_map(corpus, content_transformer(tolower))  
corpus <- tm_map(corpus, removePunctuation)            
corpus <- tm_map(corpus, removeNumbers)               
corpus <- tm_map(corpus, removeWords, all_stopwords) 

# Create a Term Document Matrix
tdm <- TermDocumentMatrix(corpus)

# Convert TDM to matrix and compute word frequencies
m <- as.matrix(tdm)
word_freq <- sort(rowSums(m), decreasing = TRUE)
word_freq_df <- data.frame(word = names(word_freq), freq = word_freq)

# Plot
ggplot(word_freq_df, aes(label = word, size = freq)) +
  geom_text_wordcloud() +
  labs(title = "Word Cloud of Speaker Feedback") +
  theme_minimal()

ggsave("../outputs/word_cloud.png", width = 8, height = 6)



```

# Pre- and post-test analyses

## Set-up

```{r}

# Load the dataset
pre_post_test_df_raw <- read_csv("../data/pre_post_test_scores_spring_2023_fall_2023.csv", show_col_types = FALSE)

```

## Clean

```{r}

# Clean data

# Rename columns for clarity
pre_post_test_df_clean <- pre_post_test_df_raw %>%
  rename(
    Semester = `Semester`,
    Test_Type = `Test Type`,
    STEM_Topic = `STEM Topic`,
    Class = `Class`,
    Total_Students = `Total Students`,
    Correct = `# correct`,
    Percent = `%`
  )


# Convert "N/A" to NA
pre_post_test_df_clean[pre_post_test_df_clean == "N/A"] <- NA


# Convert necessary columns to numeric
pre_post_test_df_clean <- pre_post_test_df_clean %>%
  mutate(
    Total_Students = as.numeric(Total_Students),
    Correct = as.numeric(Correct),
    Percent = as.numeric(Percent)
  )

# Filter for Fall 2023
pre_post_test_df_fall_2023_clean <- pre_post_test_df_clean %>% dplyr::filter(Semester == "Fall 2023")


# Add rows

pre_post_test_df_fall_2023_clean <- pre_post_test_df_fall_2023_clean %>%
  mutate(
    Test_Type = factor(Test_Type, levels = c("Pre-Test", "Post-Test")),
    Class     = factor(Class,     levels = c("K-2", "3-5"))
  )

head(pre_post_test_df_fall_2023_clean)

# Median by class and test type
pre_post_test_df_fall_2023_clean %>%
  group_by(Class, Test_Type) %>%
  summarize(Median_Score = median(Percent, na.rm = TRUE), .groups = "drop") %>%
  print()


```

### Fall 2023 by grade group

```{r}

# Reshape
pre_post_test_df_fall_2023_clean_wide <- pre_post_test_df_fall_2023_clean %>%
  select(Semester, Class, STEM_Topic, Test_Type, Percent) %>%
  pivot_wider(names_from = Test_Type, values_from = Percent, names_prefix = "Test_") %>%
  rename(Test_Pre = `Test_Pre-Test`, Test_Post = `Test_Post-Test`) %>% 
  drop_na() 


head(pre_post_test_df_fall_2023_clean_wide)


# Unpaired t-tests (as described in write-up)
k2_data <- pre_post_test_df_fall_2023_clean_wide %>% dplyr::filter(Class == "K-2")

t.test(k2_data$Test_Pre, k2_data$Test_Post, paired = FALSE)

grades35_data <- pre_post_test_df_fall_2023_clean_wide %>% dplyr::filter(Class == "3-5")

t.test(grades35_data$Test_Pre, grades35_data$Test_Post, paired = FALSE)


# Visual deficiency friendly pallette
okabe_ito <- palette.colors(palette = "Okabe-Ito")
test_colors <- c("Pre-Test" = okabe_ito[2], "Post-Test" = okabe_ito[3])


# Plot
ggplot(pre_post_test_df_fall_2023_clean, aes(x = Test_Type, y = Percent, fill = Test_Type)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(alpha = 0.3, width = 0.2) +
  facet_wrap(~ Class) +
  scale_fill_manual(values = test_colors) +
  labs(title = "Pre-Test vs. Post-Test Percentages (Fall 2023)", x = "", y = "Percent (%)") +
  ylim(0,100) +
  theme_bw() +
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))




```

### Fall 2023

```{r}

# Aggregate K-5 together
pre_post_test_df_fall_2023_k_5_clean <- pre_post_test_df_fall_2023_clean %>%
  select(Test_Type, Percent) %>%
  mutate(Test_Type = factor(Test_Type, levels = c("Pre-Test", "Post-Test")))

# Median by test type
pre_post_test_df_fall_2023_k_5_clean %>%
  group_by(Test_Type) %>%
  summarize(Median_Score = median(Percent, na.rm = TRUE), .groups = "drop") %>%
  print()

```

```{r}

# Unpaired t-test
pre_scores  <- pre_post_test_df_fall_2023_k_5_clean %>% 
  dplyr::filter(Test_Type == "Pre-Test")  %>% 
  pull(Percent)

post_scores <- pre_post_test_df_fall_2023_k_5_clean %>% 
  dplyr::filter(Test_Type == "Post-Test") %>% 
  pull(Percent)

t.test(pre_scores, post_scores, paired = FALSE, var.equal = TRUE)

```

```{r}

# Plot
ggplot(pre_post_test_df_fall_2023_k_5_clean, aes(x = Test_Type, y = Percent, fill = Test_Type)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(alpha = 0.3, width = 0.2) +
  scale_fill_manual(values = test_colors) +
  labs(title = "Pre-Test vs. Post-Test Percentages (K-5 aggregated, Fall 2023)",
       x = "", y = "Percent (%)") +
  ylim(0,100) +
  theme_bw() +
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))

ggsave("../outputs/k5_pre_post_test_comparison.png", width = 7.29, height = 4.5, dpi = 300)


```

### Spring 2023 vs. Fall 2023 by grade group

```{r}

# Calculate per-topic improvement
improvement_data <- pre_post_test_df_clean %>%
  select(Semester, Class, STEM_Topic, Test_Type, Percent) %>%
  pivot_wider(names_from = Test_Type, values_from = Percent) %>%
  mutate(Improvement = `Post-Test` - `Pre-Test`,
         Semester = factor(Semester, levels = c("Spring 2023", "Fall 2023"))) %>%
  drop_na()

# Compute n per Semester × Class for labels
n_labels <- improvement_data %>%
  group_by(Semester, Class) %>%
  summarize(n = n(), label = paste0("n = ", n()), .groups = "drop")

# Plot
okabe_ito <- palette.colors(palette = "Okabe-Ito")
semester_colors <- c("Spring 2023" = okabe_ito[2], "Fall 2023" = okabe_ito[3])

ggplot(improvement_data, aes(x = Semester, y = Improvement, fill = Semester)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(alpha = 0.3, width = 0.2) +
  geom_text(data = n_labels, aes(x = Semester, y = -Inf, label = label),
            vjust = -0.5, size = 3, inherit.aes = FALSE) +
  facet_wrap(~ Class) +
  scale_fill_manual(values = semester_colors) +
  labs(title = "Pre- to Post-Test by Semester and Grade Group",
       x = "Semester", y = "Improvement (%)") +
  ylim(0,100) +
  theme_bw() +
  theme(legend.position = "none")

ggsave("../outputs/faceted_pre_post_test_improvement.png", width = 7.29, height = 4.5, dpi = 300)


```

### Spring 2023 vs. Fall 2023

```{r}

# Aggregated improvement
improvement_data_k5 <- pre_post_test_df_clean %>%
  select(Semester, Class, STEM_Topic, Test_Type, Percent) %>%
  pivot_wider(names_from = Test_Type, values_from = Percent) %>%
  mutate(Improvement = `Post-Test` - `Pre-Test`,
         Semester = factor(Semester, levels = c("Spring 2023", "Fall 2023"))) %>%
  drop_na()

# n per Semester
n_labels_k5 <- improvement_data_k5 %>%
  group_by(Semester) %>%
  summarize(label = paste0("n = ", n()), .groups = "drop")

# Plot
ggplot(improvement_data_k5, aes(x = Semester, y = Improvement, fill = Semester)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(alpha = 0.3, width = 0.2) +
  geom_text(data = n_labels_k5, aes(x = Semester, y = -Inf, label = label),
            vjust = -0.5, size = 3, inherit.aes = FALSE) +
  scale_fill_manual(values = semester_colors) +
  labs(title = "Pre- to Post-Test Improvement by Semester (K-5 Aggregated)",
       x = "Semester", y = "Improvement (%)") +
  ylim(0,100) +
  theme_bw() +
  theme(legend.position = "none")

ggsave("../outputs/k5_pre_post_test_improvement.png", width = 7.29, height = 4.5, dpi = 300)

```

```{r}
# Load the dataset
data <- read_csv("../data/favorite_activities_fall_2023.csv", show_col_types = FALSE)

# Calculate total votes per activity & standard deviation
data_summary <- data %>%
  group_by(Activity, Topic) %>%
  summarize(
    Total_Votes = sum(Votes, na.rm = TRUE),
    SD_Votes = sd(Votes, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    Percent_Votes = (Total_Votes / sum(Total_Votes)) * 100,
    SD_Percent = (SD_Votes / sum(Total_Votes)) * 100
  )

data_summary

# Table output

table_export <- data_summary %>%
  arrange(desc(Percent_Votes)) %>%
  mutate(
    Percent_Votes = round(Percent_Votes, 2),
    SD_Percent = round(SD_Percent, 2)
  ) %>%
  select(Activity, Topic, Total_Votes, Percent_Votes, SD_Percent)

# Print to console in clean format
print(table_export)

# Define Okabe-Ito color palette based on topics
topic_colors <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442",
                  "#0072B2", "#D55E00", "#CC79A7", "#999999")

# Create the bar plot
ggplot(data_summary, aes(x = reorder(Activity, Percent_Votes), y = Percent_Votes, fill = Topic)) +
  geom_bar(stat = "identity", width = 0.7) +
  geom_errorbar(aes(ymin = Percent_Votes, ymax = Percent_Votes + SD_Percent), width = 0.2) +
  coord_flip() +
  scale_fill_manual(values = topic_colors) +
  labs(
    title = "Favorite Activities for K-5",
    x = "Activity",
    y = "Percentage of Total Votes"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

# Save plot
ggsave("../outputs/favorite_activities_by_topic_k5.png", width = 8, height = 6, dpi = 300)




```

```{r}

# Perform ANOVA
anova_result <- aov(Votes ~ Activity, data = data)
summary(anova_result)

# Perform Tukey HSD test
tukey_result <- TukeyHSD(anova_result)

# Print Tukey HSD results
print(tukey_result)

# Plot
plot(tukey_result)


```

```{r}


# Load the dataset data <- read_csv("../data/favorite_topics_fall_2023.csv", show_col_types = FALSE) # Compute percentages for the donut chart data <- data %>% mutate( Fraction = Votes / sum(Votes), ymax = cumsum(Fraction), ymin = c(0, head(ymax, -1)), LabelPosition = (ymax + ymin) / 2, Label = paste0(str_wrap(Topic, width = 12), "\n", round(Fraction * 100, 1), "%") # Wrapped text ) # ANOVA test to compare votes across topics anova_results <- aov(Votes ~ Topic, data = data) anova_summary <- summary(anova_results) # Print ANOVA results print("ANOVA Results for Favorite Topics:") print(anova_summary) # Plot the donut chart ggplot(data, aes(ymax = ymax, ymin = ymin, xmax = 4, xmin = 3, fill = Topic)) + geom_rect(color = "white") + geom_text(aes(x = 3.5, y = LabelPosition, label = str_wrap(Label, width = 10)), size = 3) + scale_fill_manual(values = wes_palette("Darjeeling1", n = nrow(data), type = "continuous")) + # Chosen bc Darjeeling1 is colorblind friendly coord_polar(theta = "y") + xlim(c(2, 4)) + # Controls thickness of the donut theme_void() + theme( legend.position = "none", plot.title = element_text(size = 14, hjust = 0.5) ) + labs(title = "Favorite Topics for K-5") # Save the plot ggsave("../outputs/favorite_topics_k5.png", width = 8, height = 6, dpi = 300)

```

```{r}

# Load the dataset
data <- read_csv("../data/favorite_topics_fall_2023.csv", show_col_types = FALSE)

# Compute percentages for the donut chart
data <- data %>%
  mutate(
    Fraction = Votes / sum(Votes),
    ymax = cumsum(Fraction),
    ymin = c(0, head(ymax, -1)),
    LabelPosition = (ymax + ymin) / 2,
    Label = paste0(str_wrap(Topic, width = 12), "\n", round(Fraction * 100, 1), "%")  # Wrapped text
  )

# ANOVA test to compare votes across topics
anova_results <- aov(Votes ~ Topic, data = data)
anova_summary <- summary(anova_results)

# Print ANOVA results
print("ANOVA Results for Favorite Topics:")
print(anova_summary)

# Define Okabe-Ito palette
okabe_ito_colors <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442",
                      "#0072B2", "#D55E00", "#CC79A7", "#999999")

# Plot the donut chart
ggplot(data, aes(ymax = ymax, ymin = ymin, xmax = 4, xmin = 3, fill = Topic)) +
  geom_rect(color = "white") +
  geom_text(
    aes(
      x = 3.5,
      y = LabelPosition,
      label = str_wrap(Label, width = 10)
    ),
    size = 3,
    family = "serif"
  ) + 
  scale_fill_manual(values = okabe_ito_colors) +
  coord_polar(theta = "y") +
  xlim(c(2, 4)) +  # Controls thickness of the donut
  theme_void() +
  theme(
    legend.position = "none",
    plot.title = element_text(size = 14, hjust = 0.5)
  ) +
  labs(title = "Favorite Topics for K-5")

# Save the plot
ggsave("../outputs/favorite_topics_k5.png", width = 8, height = 6, dpi = 300)


```

```{r}

# Load the dataset
attendance <- read_csv("../data/fall_2023_attendance.csv", show_col_types = FALSE)

# Calculate percentage attendance
attendance <- attendance %>%
  mutate(Percent_Attended = (Attended / Total_lessons) * 100) %>%
  dplyr::filter(!is.na(Percent_Attended))

# Summary statistics by grade
attendance_summary <- attendance %>%
  group_by(Grade) %>%
  summarize(
    Avg_Attended = mean(Attended, na.rm = TRUE),
    Avg_Percent = mean(Percent_Attended, na.rm = TRUE),
    SD_Attended = sd(Attended, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  )

# Order the grades to ensure Kindergarten appears first
attendance$Grade <- factor(attendance$Grade, levels = c("Kindergarten", "1st", "2nd", "3rd", "4th", "5th", "6th"))

# Define color palette (Remove black from Okabe-Ito)
okabe_ito_colors <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")  # Excluding black

# Boxplot of attendance by grade
ggplot(attendance, aes(x = Grade, y = Percent_Attended, fill = Grade)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(alpha = 0.4, color = "gray30", width = 0.2) +  # Use dark gray for better visibility
  scale_fill_manual(values = okabe_ito_colors) +
  labs(
    title = "Attendance Distribution by Grade",
    x = "Grade",
    y = "Attendance (%)"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

# Bar plot of average attendance by grade
ggplot(attendance_summary, aes(x = Grade, y = Avg_Percent, fill = Grade)) +
  geom_bar(stat = "identity", width = 0.7) +
  scale_fill_manual(values = okabe_ito_colors) +
  geom_errorbar(
    aes(ymin = Avg_Percent - SD_Attended, ymax = Avg_Percent + SD_Attended),
    width = 0.2
  ) +
  labs(
    title = "Average Attendance by Grade",
    x = "Grade",
    y = "Average Attendance (%)"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

# Create a formatted table using gt
attendance_table <- attendance_summary %>%
  gt() %>%
  tab_header(
    title = "Attendance Summary by Grade",
    subtitle = "Fall 2023 Attendance Data"
  ) %>%
  cols_label(
    Grade = "Grade",
    Avg_Attended = "Avg. Lessons Attended",
    Avg_Percent = "Avg. Attendance (%)",
    SD_Attended = "Standard Deviation",
    n = "Sample Size (n)"
  ) %>%
  tab_spanner(
    label = "Attendance Metrics",
    columns = c(Avg_Attended, Avg_Percent, SD_Attended)
  ) %>%
  fmt_number(
    columns = c(Avg_Attended, Avg_Percent, SD_Attended),
    decimals = 2
  ) %>%
  tab_footnote(
    footnote = "Percentages and averages calculated based on total lessons attended.",
    locations = cells_column_labels(columns = Avg_Percent)
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_spanners()
  ) %>%
  tab_options(
    table.font.size = 12,
    column_labels.font.size = 14
  )

# Print the table
attendance_table

```

```{r}

library(tidyverse)
library(lubridate)

attendance <- read_csv("../data/attendance_full.csv", show_col_types = FALSE)

# --------------------------------------------------
# 1. Wide → long (select date cols explicitly by pattern)
# --------------------------------------------------
attendance_long <- attendance %>%
  select(Grade, Student, matches("^\\d+/\\d+$")) %>%  # keep only m/d cols
  pivot_longer(
    cols      = -c(Grade, Student),
    names_to  = "Date",
    values_to = "Present"
  ) %>%
  mutate(
    Date = mdy(paste0(Date, "/2023")),
    Week = floor_date(Date, "week"),
    Day  = if_else(wday(Date) < 4, "Day 1", "Day 2")
  )

# --------------------------------------------------
# 2. Grade grouping
# --------------------------------------------------
attendance_long <- attendance_long %>%
  mutate(
    Grade_Group = case_when(
      Grade %in% c("Kindergarten", "1st", "2nd") ~ "K-2",
      Grade %in% c("3rd", "4th", "5th")          ~ "3-5",
      TRUE                                         ~ "Other"
    )
  )

# --------------------------------------------------
# 3. Summary table
# --------------------------------------------------
attendance_summary_table <- attendance_long %>%
  group_by(Week, Day, Grade_Group) %>%
  summarize(
    Students_Present = sum(Present, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_wider(
    names_from  = Grade_Group,
    values_from = Students_Present
  ) %>%
  arrange(Week, Day)

print(attendance_summary_table)

```

```{r}

# Perform ANOVA
attendanceANOVA <- lm(Percent_Attended ~ Grade, data = attendance)
anova_results <- anova(attendanceANOVA)

# Print
print("ANOVA Results:")
print(anova_results)

# Tukey's Honest Significant Difference test
tukey_results <- TukeyHSD(aov(attendanceANOVA))

# Print
print("Tukey HSD Results:")
print(tukey_results)

# Plot
plot(tukey_results, las = 1)


```

```{r}


# Read in the attendance dataset
attendance_full <- read_csv("../data/attendance_full.csv", show_col_types = FALSE)

# Convert wide format to long format (pivot attendance data)
attendance_long <- attendance_full %>%
  pivot_longer(cols = -c(Grade, Student), names_to = "Date", values_to = "Attended")

# Convert TRUE/FALSE attendance values to numeric (1 = attended, 0 = absent)
attendance_long <- attendance_long %>%
  mutate(
    Attended = as.numeric(Attended), 
    Date = as.Date(Date, format = "%m/%d")  # Convert to Date format
  )

# Ensure that Date conversion worked
print(unique(attendance_long$Date))  # Check the unique dates

# If Date is not in the correct format, try:
attendance_long <- attendance_long %>%
  mutate(Date = as.Date(Date, format = "%m/%d", origin = "2023-01-01"))

# Calculate cumulative attendance decline over time
attendance_summary <- attendance_long %>%
  group_by(Date) %>%
  summarize(
    Attendance_Rate = mean(Attended, na.rm = TRUE) * 100  # Convert proportion to percentage
  ) %>%
  arrange(Date) %>%  # Ensure correct chronological order
  mutate(
    Attendance_Change = c(NA, diff(Attendance_Rate)),  # Compute rate of attendance change
    Cumulative_Decline = 100 - Attendance_Rate  # Track cumulative decline
  )


# Plot attendance trends over time (Original trend)
p1 <- ggplot(attendance_summary, aes(x = Date, y = Attendance_Rate)) +
  geom_line() +
  geom_point() +
  labs(
    title = "Attendance Trends Over Time",
    x = "Date",
    y = "Attendance Rate (%)"
  ) 

p1

# Plot rate of change of attendance (How quickly students are leaving)
p2 <- ggplot(attendance_summary, aes(x = Date, y = Attendance_Change)) +
  geom_line() +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed") +  # Reference line for no change
  labs(
    title = "Rate of Change in Attendance Over Time",
    x = "Date",
    y = "Change in Attendance Rate (%)"
  ) 

p2

# Save the plots
ggsave("../outputs/attendance_trends_over_time.png", plot = p1, width = 7.5, height = 5, dpi = 300)
ggsave("../outputs/attendance_rate_of_change.png", plot = p2, width = 7.5, height = 5, dpi = 300)



```

```{r}

# Calculate overall attendance rate
overall_attendance_rate <- attendance_long %>%
  summarize(Overall_Attendance_Rate = mean(Attended, na.rm = TRUE) * 100) %>%
  pull(Overall_Attendance_Rate)

# Print the overall attendance rate
print(paste("Overall Attendance Rate:", round(overall_attendance_rate, 2), "%"))


```

```{r}

# Box and Whisker Plot (Jittered)

# Load the dataset
data <- read_csv("../data/pre_post_test_scores_spring_2023_fall_2023.csv", show_col_types = FALSE)

# Rename columns for clarity
data <- data %>%
  rename(
    Semester = `Semester`,
    Test_Type = `Test Type`,
    STEM_Topic = `STEM Topic`,
    Class = `Class`,
    Total_Students = `Total Students`,
    Correct = `# correct`,
    Percent = `%`
  )

# Convert N/A to NA
data[data == "N/A"] <- NA

# Convert necessary columns to numeric
data <- data %>%
  mutate(
    Total_Students = as.numeric(Total_Students),
    Correct = as.numeric(Correct),
    Percent = as.numeric(Percent)
  )



# Separate pre and post-tests
pre_tests <- data %>% dplyr::filter(Test_Type == "Pre-Test")
post_tests <- data %>% dplyr::filter(Test_Type == "Post-Test")

# Join pre and post-tests
improvement_data <- pre_tests %>%
  rename(Pre_Total_Students = Total_Students, Pre_Correct = Correct, Pre_Percent = Percent) %>%
  left_join(post_tests %>%
              rename(Post_Total_Students = Total_Students, Post_Correct = Correct, Post_Percent = Percent),
            by = c("Semester", "STEM_Topic", "Class"))

# Calculate improvement and remove NA values
improvement_data <- improvement_data %>%
  mutate(Improvement = as.numeric(Post_Percent) - as.numeric(Pre_Percent)) %>%
  select(Semester, Class, Improvement) %>%
  drop_na()

# Convert Semester into an ordered factor to control display order
improvement_data$Semester <- factor(improvement_data$Semester, levels = c("Spring 2023", "Fall 2023"))

# Plot the overall improvement, faceted by Class (K-2 and 3-5)
ggplot(improvement_data, aes(x = Semester, y = Improvement, fill = Semester)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(alpha = 0.3, width = 0.2) +
  facet_wrap(~ Class) +
  labs(
    title = "Overall Improvement from Pre to Post Test by Semester and Class",
    x = "Semester",
    y = "Improvement (%)"
  ) +
  theme(legend.position = "none")

# Save the plot
ggsave("../outputs/faceted_pre_post_test_improvement.png", width = 7.29, height = 4.5, dpi = 300)


```

```{r}

library(tidyverse)
library(lubridate)
library(gt)

# Load and rename columns
data_raw <- read_csv("../data/Combined_Speaker_Surveys.csv", show_col_types = FALSE)

colnames(data_raw) <- c(
  "Timestamp", "Name", "Subject", "Speaker_Before", "Overall_Rating",
  "Inspire_Info", "Hands_On_Activities", "Background_Knowledge",
  "Engagement_Enjoyment", "Staff_Helpfulness", "Went_Well", "Went_Not_Well",
  "Speaker_Quote", "Future_Suggestions", "Email"
)

# Clean and tag by time period
data <- data_raw %>%
  mutate(
    Timestamp = parse_date_time(Timestamp, orders = c("mdy HMS", "ymd HMS", "mdy HM", "ymd HM", "Ymd HMS", "Ymd HM", "Ymd IMp")),
    Period = if_else(Timestamp < ymd("2023-08-01"), "Before", "After"),
    Background_Knowledge = as.numeric(Background_Knowledge) * 2,
    Engagement_Enjoyment = Engagement_Enjoyment * 2,
    Staff_Helpfulness = Staff_Helpfulness * 2
  )

# Summarize responses
summary_table <- data %>%
  select(Period, Overall_Rating, Background_Knowledge, Engagement_Enjoyment, Staff_Helpfulness) %>%
  pivot_longer(-Period, names_to = "Question", values_to = "Response") %>%
  group_by(Period, Question) %>%
  summarize(
    Mean = round(mean(Response, na.rm = TRUE), 2),
    SD = round(sd(Response, na.rm = TRUE), 2),
    n = sum(!is.na(Response)),
    .groups = "drop"
  )

# Pivot wider for final output
summary_table_wide <- summary_table %>%
  pivot_wider(names_from = Period, values_from = c(Mean, SD, n))

# Display as gt table
summary_table_wide %>%
  gt() %>%
  tab_header(
    title = "Lesson Ratings by Period",
    subtitle = "Comparison Before and After Fall 2023"
  ) %>%
  fmt_number(columns = where(is.numeric), decimals = 2) %>%
  tab_footnote(
    footnote = "All values scaled to a max of 10. Includes only numeric feedback questions.",
    locations = cells_column_labels(columns = everything())
  )


summary_table_wide

# Drop NAs before running t-test
before <- na.omit(data$Background_Knowledge[data$Period == "Before"])
after <- na.omit(data$Background_Knowledge[data$Period == "After"])

# Run t-test
t_test_result <- t.test(before, after, paired = FALSE, var.equal = TRUE)
print(t_test_result)

# Make sure 'Period' is a factor with correct order
data$Period <- factor(data$Period, levels = c("Before", "After"))

# Boxplot
ggplot(data, aes(x = Period, y = Background_Knowledge, fill = Period)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.2, alpha = 0.3) +
  labs(
    title = "Background Knowledge Ratings Before vs. After Fall 2023",
    x = "Period",
    y = "Rating (Scaled 1–10)"
  ) +
  theme_minimal() +
  theme(legend.position = "none") +
  ylim(0, 10)


# Save the plot
ggsave("../outputs/background_knowledge_comparison.png", width = 7, height = 4.5, dpi = 300)





```

```{r}

# Subset and drop NA values
before <- data %>%
  dplyr::filter(Period == "Before") %>%
  pull(Background_Knowledge) %>%
  na.omit()

after <- data %>%
  dplyr::filter(Period == "After") %>%
  pull(Background_Knowledge) %>%
  na.omit()

# Check sample sizes first
cat("n Before:", length(before), "\n")
cat("n After:", length(after), "\n")

```
